Automatic Matching of Bullet Lands

### 2016-01-08 imaging-paper.Rnw
added acknowledgement

\section*{Acknowledgment} 
Thanks to the men and women behind the software R~\citep{R}, and the authors of the R packages  knitr~\citep{knitr} and ggplot2~\citep{ggplot2}.

>>>>

\section*{Acknowledgment} 
%Thanks to David Baldwin for pointing us to the NIST database and introducing us to the basic terms.
Thanks to the men and women behind the software R~\citep{R}, and the authors of the R packages  knitr~\citep{knitr} and ggplot2~\citep{ggplot2}.
